### 2019-06-05 doc/chapters/introduction.tex
added subtitles
updated intro

In this work we experiment in formal verification of Scala code. 
We use the verification framework Stainless to verify parts of the code of Bitcoin-S, a Scala implementation of the Bitcoin protocol.
In the following we describe the main aspects of formal verification, Stainless and Bitcoin-S.

@@

>>>>

In this work we use the verification framework Stainless to verify parts of the code of Bitcoin-S, a Scala implementation of the Bitcoin protocol.
In the following we describe the main aspects of formal verification, Stainless and Bitcoin-S.

@@

\subsection{No Inflation Property}

\subsection{Addition with Zero Property}
